A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2021-02-27 index.Rmd
Rework title for clarity
update headings

---
title: "Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis."
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: "Mungbean.bib"
biblio-style: apalike
link-citations: yes
github-repo: OpenPlantPathology/Mungbean_PM
description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
---
# Home

@@

   1. [Details of the experiments, which were included in the analysis][Studies considered in meta-analysis]  
   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  
      a. [Fungicides][Fungicides]  
      b. [Mungbean cultivar][Mungbean cultivars]  
      c. [Row spacing][Row spacing]  
      d. [Rainfall][Yield vs in-season rain]  
      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
   4. [Meta-analysis of the effect of fungicide spray schedule on yield loss][Meta-analysis]  
   5. [Meta-analysis of the effect of fungicide spray schedule on disease severity and yield loss][AUPDC meta-analysis]
   6. [Manuscript Wireframe][Manuscript wire frame]
   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]

>>>>

---
title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: "Mungbean.bib"
biblio-style: apalike
link-citations: yes
github-repo: OpenPlantPathology/Mungbean_PM
description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
---
# Home

@@

   1. [Details of the experiments, and application of inclusion criteria in the analysis][Trials considered for inclusion in meta-analysis]  
      a. [Inclusion criteria][Criteria for inclusion in meta-analysis]
      b. [Import data][Import data]
      c. [Trial summary][Summary of all trials]
      d. [Locations of considered trials][Experiment locations]
      e. [Apply selection criteria][Subset data to selection criteria]
      f. [Classifing moderator variable - spray schedule][Classifying spray schedule]
      g. [Identifing treatment variance][Identify variance]
   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  
      a. [Fungicides][Fungicides]  
      b. [Mungbean cultivar][Mungbean cultivars]  
      c. [Row spacing][Row spacing]  
      d. [Rainfall][Yield vs in-season rain]  
      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
   4. [Meta-analysis of the effect of fungicide spray schedule on yield loss][Meta-analysis]  
   5. [Meta-analysis of the effect of fungicide spray schedule on disease severity and yield loss][AUPDC meta-analysis]
   6. [Manuscript Wireframe][Manuscript wire frame]
   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]
